Proper radial distance as a coordinate in the Schwarzschild metric

### 2022-06-16 arxiv/template.tex
include spacetime diagrams

\usepackage{arxiv}

\usepackage[utf8]{inputenc} % allow utf-8 input
\usepackage[T1]{fontenc}    % use 8-bit T1 fonts
\usepackage{hyperref}       % hyperlinks
\usepackage{url}            % simple URL typesetting
\usepackage{booktabs}       % professional-quality tables
\usepackage{amsfonts}       % blackboard math symbols
\usepackage{nicefrac}       % compact symbols for 1/2, etc.
\usepackage{microtype}      % microtypography
\usepackage{cleveref}       % smart cross-referencing
\usepackage{lipsum}         % Can be removed after putting your text content
\usepackage{graphicx}
\usepackage{natbib}
\usepackage{doi}
\title{Proper radial distance as a coordinate in the Schwarzschild metric}

@@

\begin{equation}
  ds^2=-dt^2\left(1-\frac{2GM}{c^2r}\right)
<  +\frac{dr^2}{\left(1-\frac{2GM}{c^2r}\right)} + r^2(\sin^2\theta
  d\phi^2 + d\theta^2)
\end{equation}

@@

\citep{hankin2021} shows that

\citet{hankin2021} shows that

\cite{hankin2020}

@@

for $w\gg 1$.

>>>>

\usepackage{arxiv}
\usepackage[utf8]{inputenc} % allow utf-8 input
\usepackage[T1]{fontenc}    % use 8-bit T1 fonts
\usepackage{hyperref}       % hyperlinks
\usepackage{url}            % simple URL typesetting
\usepackage{booktabs}       % professional-quality tables
\usepackage{amsfonts}       % blackboard math symbols
\usepackage{nicefrac}       % compact symbols for 1/2, etc.
\usepackage{microtype}      % microtypography
\usepackage{cleveref}       % smart cross-referencing
\usepackage{lipsum}         % Can be removed after putting your text content
\usepackage{graphicx}
\usepackage{natbib}
\usepackage{doi}
\usepackage{caption}
\usepackage{subcaption}
\title{Proper radial distance as a coordinate in the Schwarzschild metric}

@@

\begin{equation}
  ds^2=-dt^2\left(1-\frac{2GM}{c^2r}\right)
  +\frac{dr^2}{\left(1-\frac{2GM}{c^2r}\right)} + r^2(\sin^2\theta
  d\phi^2 + d\theta^2)
\end{equation}

@@

% \citep{hankin2021} \citet{hankin2021}

@@

for $w\gg 1$.  We can use this as a coordinate on the same footing as
circumferential radius $r$.  The first thing to do would be to
suppress $\theta,\phi$ coordinates and consider only $r,t$; see
Figures~\ref{schwarzschild} and~\ref{eddington}.

\begin{figure}%
    \centering
    \subfloat{{\includegraphics[width=7cm]{schwarzschild.pdf} }}%produced by the schwarzschild package
    \subfloat{{\includegraphics[width=7cm]{schwarzschild_stringcoords.pdf} }}%
    \caption{Spacetime near a black hole with $\theta,\phi$
      suppressed.  Left, diagram in $r,t$ coordinates.  Right, same
      spacetime but presented in $u_1,t$ coordinates: note absence of interior on right}
    \label{schwarzschild}%
\end{figure}

\begin{figure}%
    \centering
    \subfloat{{\includegraphics[width=7cm]{eddington.pdf} }}%
    \subfloat{{\includegraphics[width=7cm]{eddington_stringcoords.pdf} }}%
    \caption{Spacetime near a black hole with $\theta,\phi$ suppressed
      using Eddington-Finkelstein coordinates.  Left, diagram in $r,t$
      coordinates.  Right, same spacetime but presented in $u_1,t$
      coordinates: note absence of interior on right}
    \label{eddington}%
\end{figure}

\begin{figure}%
    \centering
    \subfloat{{\includegraphics[width=7cm]{gullstrand.pdf} }}%
    \subfloat{{\includegraphics[width=7cm]{gullstrand_stringcoords.pdf} }}%
    \caption{Spacetime near a black hole with $\theta,\phi$ suppressed
      using Gullstrand coordinates.  Left, diagram in $r,t$
      coordinates.  Right, same spacetime but presented in $u_1,t$
      coordinates: note absence of interior on right}
    \label{gullstrand}%
\end{figure}
